\documentclass[12pt]{article}
\pagestyle{empty}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{latexsym, epsfig, ulem, cancel, multicol, hyperref}
\usepackage{graphicx, tikz, subfigure,pgfplots}
\usepackage[margin=1in]{geometry}
\setlength{\parindent}{0pt}
\usepackage{multirow}
\usepackage{mathtools}


\newcommand{\R}{\mathbb{R}}
\newcommand{\dydx}{\frac{dy}{dx}}
\usepackage{verbatim}
\usepackage{tikz}
\usepackage{pgfplots}

\newcommand{\wsnumber}{1}
\newcommand{\wstopic}{Vectors}
\pgfplotsset{
    every linear axis/.append style={
       axis x line=center,
       axis y line=center,
       xlabel={$x$},
       ylabel={$y$}
    },
    every axis plot/.append style={thick,mark=none}
}
\tikzset{
    point/.style={circle,draw,fill,minimum width=0.3ex,inner sep=0pt,outer sep=0pt},
    every label/.append style={black}
}


\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amssymb, amsthm, graphicx, hyperref}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{multirow, multicol}
\usepackage{tikz}
\pagestyle{fancy}
\fancyhead[RO]{Spring 2024}
\fancyhead[LO]{MA-UY 3113 Complex Variables and Linear Algebra }
\usepackage{comment}
\newif\ifshow
\showfalse

\ifshow
  \newenvironment{solution}{\textbf{Solution.}}{}
\else
  \excludecomment{solution}
\fi

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\usepackage{comment}


\newtheorem*{remark}{Remark}


\begin{document}

\begin{center}
\ifshow
  \textbf{\Large Homework 5 Solution}\\
\else
  \textbf{\Large Homework 5}\\
\fi
Due: Sunday March 31, by 11:59pm,\\via Gradescope\\
\end{center}

\hrule

\vspace{0.2cm}

\begin{enumerate}[$\bullet$]
\item  {\textbf{\textit{Note that you must assign a page to each problem you submit.}}}   Gradescope has great YouTube videos available on how to submit homework.  \textit{\textbf{Failure to submit homework correctly will result in a zero on homework.}}
\item Problems that appear with the notation \colorbox{yellow}{$\ast$} will require you to TeX your solution.  If no highlighted star appears, then a hand written solution is OK.  
\item Late homework is not accepted.  Lateness due to technical issues will not be excused.  
\end{enumerate}

\hrule

\vspace{0.5cm}



\begin{enumerate}
\item Suppose that $A$ is a $5 \times 8$ matrix.  Determine whether the given set is a subspace of $\mathbb{R}^{5}$ or $\mathbb{R}^{8}$. 
\begin{enumerate}
    \item $N(A)$.
    \item $N(A^{T})$.
    \item $C(A)$.
    \item $C(A^{T})$.
    \item $N(AA^{T})$.
      \item $C(AA^{T})$.
        \item $N(A^{T}A)$.
                \item $C(A^{T}A)$.
\end{enumerate}
\\
\textbf{Solution:}
\\
\[
N(A)\in\mathbb{R}^8
\]
\[
N(A^T)\in\mathbb{R}^5
\]
\[
C(A)\in\mathbb{R}^5
\]
\[
C(A^T)\in\mathbb{R}^8
\]
\[
N(AA^T)\in\mathbb{R}^5
\]
\[
C(AA^T)\in\mathbb{R}^5
\]
\[
N(A^TA)\in\mathbb{R}^8
\]
\[
C(A^TA)\in\mathbb{R}^8
\]



    
 \item Suppose that the matrix $A$ has $n$ columns: $A = [\vec a_1 \ \ldots \ \vec a_n]$.  Also suppose that we have an additional column $\vec b$ to $A$: \[A' = [A \ \vec b].\]
\begin{enumerate}
	\item 	Then, the column space of $A'$ is equal to the column space of $A$ if\\
\[
\textbf{Answer:} \;\;\;C(A)=C(A')\iff \; \Vec{b} = [c_1\Vec{a_1}+c_2\Vec{a_2}+ \ldots c_n\vec a_n]
\]

	\item Give an example of a matrix $A$ and a vector $\vec b$ where the column space of $A'$ is larger than the column space of $A$ and an example where it is not.  
 \\
 \textbf{Solution:}\\
 \[
 \text{let}\; A=
 \begin{bmatrix}
1&0\\
0&1
 \end{bmatrix}
 \;\;\;
 \vec b\ = 
 \begin{bmatrix}
 1\\1
 \end{bmatrix}
 \]
 \[
 A'=
 \begin{bmatrix}
     1&0&1\\
     0&1&1
 \end{bmatrix}
 \]
\[ \because \;
 \Vec{b}=
\begin{bmatrix}
     0\\1
\end{bmatrix}
 +
\begin{bmatrix}
     1\\0
\end{bmatrix}
\]
\[
\therefore \; Span(C(A))=Span(C(A'))=\mathbb{R}^2
\]
\[
\text{for the other case, we let}\; B=
\begin{bmatrix}
    1&0\\
    0&1\\
    0&0
\end{bmatrix}\;\;\;
\Vec{b}=
\begin{bmatrix}
    0\\0\\1
\end{bmatrix}
\]
\[
A'=
\begin{bmatrix}
    1&0&0\\
    0&1&0\\
    0&0&1
\end{bmatrix}
\]
\[
\because \text{$\Vec{b}$ is not a linear combination of column vectors of $A$}
\]
\[
Span(C(A))=\mathbb{R}^2
\]
\[
Span(C(A'))=\mathbb{R}^3
\]
	
	\item Why is $A\vec x = \vec b$ solvable exactly when the column space doesn't get larger (i.e., when $A'$ and $A$ have the same column space).
\\
\textbf{Answer: }\\

if $C(A)$ span the same space as $C(A')$, it implies $\Vec{b}$ can be expressed as a linear combination of 
column vectors of A. And $\Vec{x}$ that satisfies $A\vec x = \vec b$ will be the matrix with components $[c_1,c_2 \ldots c_n]$
such that\\
\[
\Vec{b} = \sum_{i=1}^{n} c_i\vec a_i
\]
and if $C(A)$ span less space than $C(A')$, it means the vector $\vec b$ added new dimension to the matrix $A$, and therefore cannot be expressed as a linear combination of column vectors of $A$, hence $\vec x$ has no solution. 

\end{enumerate}







\item  \colorbox{yellow}{$\ast$}  Let $A$ be an $m \times n$ matrix and let $r$ denote the rank of $A$.

Write down all known relations between $r, m$, and $n$ if $A\vec x = \vec b$ has
	\begin{enumerate}
	\item no solution for some $\vec b$\\
        \[
        \text{if $r<m$, $\vec x$ has no solution other than the trivial solution for $\vec b\ \notin C(A)$}
        \]
	\item infinitely-many solutions for every $\vec b$
        \[
        \text{if $m<n$, $r=m$, this system is under-determined} \]\[
        \text{and $\exists$ infinitely many $\vec x\ $ for every $\vec b\ \in C(A)$}
        \]
	\item exactly one solution for some $\vec b$, no solution for other $\vec b$
        \[
        \text{if $r=n,\; n<m$}\;\; \exists! \vec x\ : A\vec x\ = \vec b\ \iff \vec b\ \in C(A)
        \]
	\item exactly one solution for every $\vec b$
        \[
        \text{if $r=m=n$, $A$ is an invertible square matrix and $\exists!\; \vec x\ =A^{-1}\vec b\  : A\vec x\ = \vec b$}
        \]
	\end{enumerate}

\end{enumerate}

\end{document}
